Test data

### 2022-07-17 Shiny/Test/Flexdashboard test.Rmd
Adding Value Box.

@@

>>>>

    # Creating value box
    KPI_admin <- reactive({exceldata() |> 
           mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
    })

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

@@

### KPI
```{r}
valueBoxOutput("KPI_box")
```

### 2022-07-17 Shiny/Test/Test data.Rmd
Adding Value Box.

### Administrative expenses
```{r}
kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  select(year, KPI_admin)
```

>>>>

### Administrative expenses
```{r}
kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  select(year, KPI_admin)

kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()

kreft_excel |> mutate(
            KPI_admin =
              expenses_administrative / expenses_program_services *100) |> 
           filter(year == max(year)) |> 
          select(KPI_admin)
```
